Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-07 Draft/contributions.tex
cosmetic corrections in section 4

% At tree level, there are three contributions to the $\PW^+\PW^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$, and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$
% \AK{We have mentioned this many times at this point. Perhaps not worth repeating again?}.
In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$, 
Eq.~(\ref{cut:4}).
In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three LO contributions are reported.
The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
The QCD contribution does not posses external gluons due to charge conservation.
Thus the diagrams of order $\mathcal{O}(\alphas^2\alpha^4)$ only involve gluon exchange in the $t/u$-channel between the quark lines.
This results in a small contribution even if the VBS cuts have not been imposed.
The interference between EW and QCD contributions is small, due to color suppression, but not negligible.
% ($t/u$ and $t/s$ interferences with identical fermions).

@@

In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distribution of the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
For the distribution in the di-jet invariant mass (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
This is due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
Note that these contributions are not present in calculations relying on the VBS approximation.
The EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$.
The same holds true for jet rapidity difference larger than $2.5$ (right).
This justifies why cuts on these two observables are used in order to enhance the EW contribution over the QCD one.
In particular, in order to have a large EW contribution, rather exclusive cuts are required.

@@

This can also be seen in Fig.~\ref{fig:mjjdyjj_2d_LO} where the three contributions are displayed as a (double-differential) function of the di-jet invariant mass and jet rapidity difference.
Again, it is obvious that the region with low di-jet invariant mass should be avoided in VBS studies as it is dominated by tri-boson contributions.
% This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study (see below).
%Finally, let us notice that the choice $m_{\Pj\Pj} > 500\GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ made by the experimental collaborations is well motivated in order to enhance the EW contribution over its irreducible backgrounds.
This motivates in particular the choice of employing the cut $m_{\Pj\Pj} > 200\GeV$ for our LO inclusive study in Sec.~\ref{subsec:LOinclusive}.

>>>>

% At tree level, there are three contributions to the $\PW^+\PW^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$, and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$
% \AK{We have mentioned this many times at this point. Perhaps not worth repeating again?}.
In the present section, the cross sections and distributions are obtained without applying the VBS cuts on the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$, 
Eq.~(\ref{cut:4}).
In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three LO contributions are reported.
The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
The QCD contribution does not posses external gluons due to charge conservation.
Thus the diagrams of order $\mathcal{O}(g_{\rm s}^2g^4)$ only involve gluon exchange in the $t/u$-channel between the quark lines.
This results in a small contribution even if the VBS cuts have not been imposed.
The interference between EW and QCD contributions is small, due to color suppression, but not negligible.
% ($t/u$ and $t/s$ interferences with identical fermions).

@@

In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
For the distribution in the di-jet invariant mass (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
This is due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
Note that these contributions are not present in calculations relying on the VBS approximation.
The EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$.
The same holds true for jet rapidity difference larger than $2.5$ (right).
This justifies why cuts on these two observables are used in order to enhance the EW contribution over the QCD one.
In particular, in order to have a large EW contribution, rather exclusive cuts are required.

@@

This can also be seen in Fig.~\ref{fig:mjjdyjj_2d_LO} where the three contributions are displayed as double-differential distributions in the di-jet invariant mass and jet rapidity difference.
Again, it is clear that the region with low di-jet invariant mass should be avoided in VBS studies as it is dominated by tri-boson contributions.
% This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study (see below).
%Finally, let us notice that the choice $m_{\Pj\Pj} > 500\GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ made by the experimental collaborations is well motivated in order to enhance the EW contribution over its irreducible backgrounds.
This motivates in particular the choice of employing the cut $m_{\Pj\Pj} > 200\GeV$ for our LO inclusive study in Sec.~\ref{subsec:LOinclusive}.
